---
title: "eddies: Package usage example"
author: "Yves Le Bras"
date: "`r Sys.Date()`"
output: knitr:::html_vignette
vignette: >
  %\VignetteIndexEntry{Package usage example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Intro 

The eddies package allow to acess to an eddy database of matlab data files downloaded 
form <http://datadryad.org/resource/doi:10.5061/dryad.gp40h/1>.

In the southern ocean, cyclonic eddies contain a cold core and rotate in clockwise 
direction.

# Example

```{r, include = FALSE}
knitr::opts_chunk$set(fig.dpi = 96)
```

```{r}
require("rbl")
require("eddies")

ses <- readRDS("F:/data/ses/post_repro/rbl/large_acc/2011-28.rds")
ses$stat$day <- floorPOSIXct(ses$stat$time)

# Setup temporal subset
days <- seq(
  from = as.POSIXct("2011-11-25", tz = "UTC"), 
  to = as.POSIXct("2011-12-12", tz = "UTC"), 
  by = "day"
  )

# Before using the package make sure that the database path is correct
# Consider setting this option in your .Rprofile if it is not the case
options("eddies.path")

# Setup geographical subset (Optional)
# options("eddies.area") <- list(
#   lon = range(ses$stat$lon), 
#   lat = range(ses$stat$lat)
#   )
# Here we will use defaults
options("eddies.area")

# Extract matching eddies from the database
edd <- eddies(days)
```

Here is an example of the result

```{r}
names(edd) # See description of these variables in ?eddies

cnd <- ses$stat$day %in% days
plot(lat ~ lon, ses$stat[cnd, ], type = "n")
plot(edd, cex = 0.5, add = TRUE)
lines(lat ~ lon, ses$stat[cnd, ], lwd = 2)
```

# Reference

Faghmous JH, Frenger I, Yao Y, Warmka R, Lindell A, Kumar V (2015) *A daily global mesoscale ocean eddy dataset from satellite altimetry*. **Scientific Data 2**: 150028. <http://dx.doi.org/10.1038/sdata.2015.28>

Faghmous JH, Frenger I, Yao Y, Warmka R, Lindell A, Kumar V (2015) *Data from: A daily global mesoscale ocean eddy dataset from satellite altimetry*. **Dryad Digital Repository**. <http://dx.doi.org/10.5061/dryad.gp40h>

